Stable Hot Spot Analysis (Draft)

### 2017-06-16 paper-main.tex
Minor fixes

We evaluate our data on the New York city yellow cab data set 
\footnote{$http://www.nyc.gov/html/tlc/html/about/trip\_record\_data.shtml$}. 
This data set includes all taxi drives from the yellow cabs in New York City, 
from location, to passengers and many more informations. In this study, we compare the 
total pickups over January from 2016 in the Manhattan area. 
The borders of the rasters are (40.699607 \textdegree  (N), -74.020265 \textdegree  (E)) and (40.769239, -73.948286).
By using this data set, we reduce the computational effort while still 
being able to show the applicability on real world data and problems.
\subsection{Treatments}

@@

  The SoH for a singled evalution run in the weight dimension is defined as:
  \begin{eqnarray*}
    child & = & G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) \\
    parent & = & G^*(R_z, W_{3+(i+1) \cdot 4}, st, F_{17+j \cdot 12}) )
  \end{eqnarray*}
  \begin{displaymath}
    z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
  \end{displaymath}
  The SoH for a singled evalution run in the focal dimension is defined as:
  \begin{eqnarray*}
    child & = & G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) \\
    parent & = & G^*(R_z, W_{3+i \cdot 4}, st, F_{17+(j+1) \cdot 12}) )
  \end{eqnarray*}
  \begin{displaymath}
    z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
  \end{displaymath}

  The SoH for a singled evalution run in the aggregation dimension is defined 
  as:
  \begin{eqnarray*}
    child & = & G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) \\
    parent & = & G^*(R_{z+1}, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) )
  \end{eqnarray*}
  \begin{displaymath}
  z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
  \end{displaymath}
\end{definition}

@@

The aggregation level is a slice plane through our three dimensional space. 
This is an example how the results can look with visualize representations of the calculated 
rasters and the raw data.
We evalute only the aggregation with fixed W and fixed F. In contrast we included the negative clusters. They where exluded for our 3 dimensional space because
the water had to much influence.
\begin{definition} Aggregation run:
\begin{displaymath}
\SOHUP( G^*(R_z, W, st, F), G^*(R_{z+1}, W, st, F) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W, st, F), G^*(R_{z+1}, W, st, F) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], dim(W)=11,dim(F)=41, G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}

@@

\subsection{Blur}
We also made an example for the variation of the weight size W.
Blur is a slice plane through our three dimensional space. 
W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
For blur we also included the negative clusters which resulted in a surprising result.
\begin{definition} Blur run:
\begin{displaymath}
\SOHUP( G^*(R_z, W_{7+i}, st, F), G^*(R_{z}, W_{7+i+2}, st, F) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_{7+i}, st, F), G^*(R_{z}, W_{7+i+2}, st, F) )
\end{displaymath}
\begin{displaymath}
z =3, i \in [1,6],dim(F)=41, G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}
The blur results are plotted in Figure~\ref{fig:Blur}. The weight matrix is
shown in the first row, with increasing size. The scond and thrid row sho how
$G^*$ and Focal $G^*$ changes based on W. This example is a slice plane of the
weight dimension ploted in figure ~\ref{fig:SoHWeight}. It can be seen that
increase of the weight size leads in general to better results for Focal $G^*$.
$G^*$ compared to the mean of our whiskerplot does not fit in the picture
because it leads to better results than $G^*$.

>>>>

We evaluate our data on the New York city yellow cab data set 
\footnote{$http://www.nyc.gov/html/tlc/html/about/trip\_record\_data.shtml$}. 
This data set includes all taxi drives from the yellow cabs in New York City, 
from location, to passengers and many more informations. In this study, we compare the 
total pickups over January from 2016 in the Manhattan area. 
The borders of the rasters are (40.699607 \textdegree  (N), -74.020265 \textdegree  (E)) 
and (40.769239 \textdegree  (N), -73.948286 \textdegree  (E)) after WGS84.
By using this data set, we reduce the computational effort while still 
being able to show the applicability on real world data and problems.
\subsection{Treatments}

@@

  The SoH for a singled evalution run in the weight dimension is defined as:
  \begin{eqnarray*}
    child & = & G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) \\
    parent & = & G^*(R_z, W_{3+(i+1) \cdot 4}, st, F_{17+j \cdot 12}) )
  \end{eqnarray*}
  The SoH for a singled evalution run in the focal dimension is defined as:
  \begin{eqnarray*}
    child & = & G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) \\
    parent & = & G^*(R_z, W_{3+i \cdot 4}, st, F_{17+(j+1) \cdot 12}) )
  \end{eqnarray*}
  The SoH for a singled evalution run in the aggregation dimension is defined 
  as:
  \begin{eqnarray*}
    child & = & G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) \\
    parent & = & G^*(R_{z+1}, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) )
  \end{eqnarray*}

  \begin{displaymath}
  z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
  \end{displaymath}
\end{definition}

@@

The aggregation level is a slice plane through our three dimensional space. 
This is an example how the results can look with visualize representations of the calculated 
rasters and the raw data.
We evalute only the aggregation with fixed W and fixed F. In contrast we included the negative clusters. They where exluded for our 3 dimensional space because
the water had to much influence.
\begin{definition} Aggregation run:
\begin{eqnarray*}
    child & = & G^*(R_z, W_11, st, F_41) \\
    parent & = & G^*(R_{z+1}, W_11, st, F_41)
  \end{eqnarray*}
\begin{displaymath}
z \in [1,6], G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}

@@

\subsection{Blur}
We also made an example for the variation of the weight size W.
Blur is a slice plane through our three dimensional space. 
W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
For blur we also included the negative clusters which resulted in a surprising result.
\begin{definition} Blur run:
\begin{eqnarray*}
    child & = & G^*(R_3, W_{7+i \cdot 2}, st, F_41) \\
    parent & = & G^*(R_3, W_{7+(i+1)\cdot 2}, st, F_41)
  \end{eqnarray*}
\begin{displaymath}
i \in [0,11], G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}
The blur results are plotted in Figure~\ref{fig:Blur}. The weight matrix is
shown in the first row, with increasing size. The scond and thrid row sho how
$G^*$ and Focal $G^*$ changes based on W. This example is a slice plane of the
weight dimension ploted in figure ~\ref{fig:SoHWeight}. It can be seen that
increase of the weight size leads in general to better results for Focal $G^*$.
$G^*$ compared to the mean of our whiskerplot does not fit in the picture
because it leads to better results than $G^*$.
